Racial and Ethnic Differences in ETI

### 2023-10-25 Kamyron Jordan/Racial and Ethnic Differences in ETI/racial_and_ethnic_differences_in_eti.qmd
smoothed plot by age
eligible only

```{r data cleaning}
#| include: false
# source("/Users/timvigers/GitHub/CF/Kamyron Jordan/Racial and Ethnic Differences in ETI/create_race_eti_analysis_dataset.R")
load("/Users/timvigers/Documents/Work/Vigers/CF/Kamyron Jordan/Racial and Ethnic Differences in ETI/Data_Cleaned/analysis_dataset.RData")
```

@@

@@

@@

```{r results='asis'}
invisible(lapply(c("2019", "2020", "2021"), function(n) {
  cat("\n")
  cat("###", n)
  cat("\n")
  d <- years[[n]]
  t <- d %>%
    select(eti_elig, contains("Vx"), race) %>%
    tbl_summary(
      by = race, missing_text = "Missing",
      type = all_dichotomous() ~ "categorical"
    ) %>%
    bold_labels()
  print(t)
  cat("\n")
}))
```

@@

>>>>

```{r data cleaning}
#| include: false
# source("/Users/timvigers/GitHub/CF/Kamyron Jordan/Racial and Ethnic Differences in ETI/create_race_eti_analysis_dataset.R")
load("~/Documents/Work/Vigers/CF/Kamyron Jordan/Racial and Ethnic Differences in ETI/Data_Cleaned/analysis_dataset.RData")
```

@@

#### All patients

@@

#### Eligible only

```{r}
annual %>%
  filter(eti_elig == "Yes") %>%
  select(contains("Vx"), ReviewYear) %>%
  tbl_summary(
    by = ReviewYear, missing_text = "Missing",
    type = all_dichotomous() ~ "categorical"
  ) %>%
  bold_labels()
```

@@

```{r results='asis'}
invisible(lapply(c("2019", "2020", "2021"), function(n) {
  cat("\n")
  cat("###", n)
  cat("\n")
  cat("\n")
  cat("#### All patients")
  cat("\n")
  d <- years[[n]]
  t <- d %>%
    select(eti_elig, contains("Vx"), race) %>%
    tbl_summary(
      by = race, missing_text = "Missing",
      type = all_dichotomous() ~ "categorical"
    ) %>%
    bold_labels()
  print(t)
  cat("\n")
  cat("\n")
  cat("#### Eligible only")
  cat("\n")
  t <- d %>%
    filter(eti_elig == "Yes") %>%
    select(contains("Vx"), race) %>%
    tbl_summary(
      by = race, missing_text = "Missing",
      type = all_dichotomous() ~ "categorical"
    ) %>%
    bold_labels()
  print(t)
  cat("\n")
}))
```

@@

```{r}
ggplot(annual, aes(x = Age_YrEnd, y = mean_ppFEV)) +
  geom_smooth(aes(color = race), se = F)
```
